openarchaeoCollaboration

### 2021-02-25 analysis/paper.Rmd
Initial analysis of contributors

```{r data-github}
oarch %>% 
  mutate(
    gh_repo = str_remove(github, "https://github.com/"),
    gh_repo = str_remove(gh_repo, "/$")
  ) %>% 
  separate(gh_repo, c("gh_owner", "gh_repo"), "/", extra = "drop") %>% 
  mutate(
    gh_lang = ght("GET /repos/{owner}/{repo}/languages", 
                  owner = gh_owner, repo = gh_repo)
  ) ->
  oarch
```

@@

What languages are people using?

@@

>>>>

```{r data-github}
# Pretty slow
oarch %>% 
  mutate(
    gh_repo = str_remove(github, "https://github.com/"),
    gh_repo = str_remove(gh_repo, "/$")
  ) %>% 
  separate(gh_repo, c("gh_owner", "gh_repo"), "/", 
           fill = "right", extra = "drop") %>% 
  mutate(
    gh_lang = ght("GET /repos/{owner}/{repo}/languages", 
                  owner = gh_owner, repo = gh_repo),
    gh_contributors = ght("GET /repos/{owner}/{repo}/contributors",
                          owner = gh_owner, repo = gh_repo)
  ) ->
  oarch
```

@@

### What languages are people using?

@@

### Who is contributing?

```{r plot-gh_contributors-by-repo}
oarch %>% 
  unnest(gh_contributors) %>% 
  mutate(gh_repo = paste(gh_owner, gh_repo, sep = "/")) %>% 
  group_by(gh_repo) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  ggplot(aes(fct_reorder(gh_repo, n, .desc = TRUE), n)) +
  geom_col() +
  labs(
    title = "Repositories by number of contributors",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = "Repository", y = "Number of contributors"
  ) +
  theme(axis.text.x = element_blank())
```
